\documentclass{article}
\usepackage[utf8]{inputenc}

\title{MHoC Member's Guide}
\author{Authors: /u/ThatThingInTheCorner, /u/Electric-Blue}
\date{December 2016}

\begin{document}

\maketitle

\section{Introduction}
Welcome to /r/MHoC!

/r/MHoC is a network of subreddits that work together to simulate how British politics works in a fun and enjoyable way.

It is centred around a network of subreddits, the two main ones being the two parlimentary chanbers, the Model House of Commons (/r/MHoC) and the Model House of Lords (/r/MHoL)

The community is headed by or head Moderator, /u/Djenial, alongside the Speaker of the House of Commons, /u/TheQuipton, and the Speaker of the House of Lords, /u/PurpleSlug

I hope this guide will give you all the information you need about how the Model Houses of Parliament works, and on behalf of the Triumvirate and the whole community, I would like to make you feel welcome to our vibrant and friendly community.

\section{Elections}
\subsection{How Elections Work}
General Elections happen around every six months. When a general election has been called, your party will have a post on their subreddit where candidates can declare their intention to stand as an MP.

By-elections also happen every so often, usually triggered when an independent MP resigns from office. There have been three by-elections so far.

Internal elections within parties are usually used to elect MPs whose predecessors have either resigned or become inactive. They are also used for leadership elections and elections for important party decisions. Please check your party's subreddit for more information as different parties have different methods of elections.

\end{document}
